\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning}

% Define Rust language for listings (not built-in)
\lstdefinelanguage{Rust}{
    keywords={fn, let, mut, pub, struct, enum, impl, self, Self, if, else, match, for, while, loop, return, break, continue, where, type, trait, const, static, ref, move, async, await, use, mod, crate, super, in, as, true, false, Ok, Err, Some, None},
    keywordstyle=\color{blue}\bfseries,
    keywords=[2]{u8, u16, u32, u64, u128, i8, i16, i32, i64, i128, f32, f64, bool, char, str, String, Vec, Option, Result, Box, Rc, Arc, H256, AccountId, BlockNumber, BoundedVec, DispatchResult, Error},
    keywordstyle=[2]\color{teal},
    sensitive=true,
    morecomment=[l]{//},
    morecomment=[s]{/*}{*/},
    morestring=[b]",
    morestring=[b]',
}

% Listings configuration
\lstset{
    language=Rust,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    commentstyle=\color{gray},
    stringstyle=\color{red!70!black},
    numbers=left,
    numberstyle=\tiny\color{gray},
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!5},
    showstringspaces=false,
    tabsize=4
}

% Theorem environments
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

% Document info
\title{Augmented Democracy as a Coherence-Constrained Control System\\
\large From Oracle Governance to Quantum-Safe Democratic Infrastructure}

\author{Sylvain Cormier\\
Paraxiom Research\\
\texttt{sylvain@paraxiom.org}}

\date{December 2025}

\begin{document}

\maketitle

\begin{abstract}
We present a systems-theoretic framework for democratic governance that treats
legitimacy as the preservation of coherence in decision-making processes rather
than as a direct consequence of majority outcomes.
The framework introduces \emph{epistemic infrastructure}---including token-curated
test grids, dynamic credential NFTs, and bounded voting weights---that restrict
participation to actors who can demonstrate verifiable engagement with relevant
evidence, without assigning semantic authority to the system itself.

Building on prior work in Hamiltonian machine learning (ERLHS), geometric
consensus (Karmonic Mesh), and quantum-safe validation (Proof of Coherence),
we formalize augmented democracy as a control system in which proposals are
state transitions, participants act as distributed sensors with bounded influence,
and acceptance requires satisfaction of both a democratic majority condition and
a coherence threshold measuring process consistency.

We trace the evolution of this framework from early conceptual work (2017),
through EOS-based smart contract implementations, to its current deployment on
the Quantum Harmony blockchain using post-quantum cryptography and quantum
entropy sources. The central claim is that democratic legitimacy is a measurable
property of process quality---independent of specific outcomes---and that governance
systems designed around epistemic admissibility and coherence constraints exhibit
improved resistance to manipulation, Sybil attacks, plutocratic capture, and
coordinated adversarial behavior.
\end{abstract}

\tableofcontents
\newpage

%------------------------------------------------------------------------------
\section{Problem: Democracy Under Adversarial Load}
\label{sec:problem}
%------------------------------------------------------------------------------

Democratic systems face compounding failure modes in the information age:

\begin{enumerate}
    \item \textbf{Unengaged voting}: Participants lack verifiable engagement with proposal-relevant evidence
    \item \textbf{Manipulation}: Coordinated influence campaigns exploit cognitive biases
    \item \textbf{Speed vs.\ legitimacy}: Rapid decisions sacrifice deliberation quality
    \item \textbf{AI-generated influence}: Large language models enable scalable persuasion
    \item \textbf{Quantum-era threats}: Future adversaries with quantum computers can
    retroactively compromise classical cryptographic commitments
\end{enumerate}

These are not political problems. They are \textit{systems failures}---the democratic control
loop lacks adequate filtering, measurement, and stability guarantees.

Traditional responses (education, regulation, fact-checking) address symptoms rather than
architecture. We require a formal framework that treats democracy as critical infrastructure
subject to engineering constraints.

%------------------------------------------------------------------------------
\section{Philosophical Foundations: Artifacts, Not Truth}
\label{sec:philosophy}
%------------------------------------------------------------------------------

Before presenting the technical framework, we establish a critical philosophical
distinction: \textbf{the governance system does not evaluate truth}. It evaluates
\textit{procedural admissibility} of evidence artifacts and \textit{process consistency}
of decision-making.

\subsection{The Semantic Authority Problem}

Any system that claims to determine ``what is true'' faces an infinite regress:
who verifies the verifiers? Classical epistemic gatekeeping (expert panels,
editorial boards, fact-checkers) ultimately rests on institutional authority
that can be captured, corrupted, or contested.

Our framework sidesteps this problem entirely. The system makes no semantic
judgments. It enforces \textit{procedural constraints} on what evidence may be
referenced and measures \textit{statistical properties} of the decision process.

\subsection{Admissible Artifacts}

\begin{definition}[Admissible Fact Artifact]
In this framework, a \emph{fact} is not treated as a semantic claim or assertion,
but as a verifiable artifact with cryptographic provenance.
An artifact is admissible for use in governance processes if it satisfies:
\begin{enumerate}
    \item \textbf{Immutable referenceability}: the artifact can be uniquely
    identified via a hash, DOI, or equivalent content-addressed reference;
    \item \textbf{Authentic issuance}: the artifact is bound to a recognized
    issuer, authority, or origin via digital signatures or equivalent mechanisms;
    \item \textbf{Contextual relevance}: the artifact belongs to an artifact
    class declared relevant for the proposal type under consideration.
\end{enumerate}
No semantic interpretation, truth evaluation, or correctness judgment is
performed by the governance system itself.
\end{definition}

This definition has important consequences:
\begin{itemize}
    \item A peer-reviewed paper is admissible because it has a DOI, is signed by
    a journal, and belongs to the ``scientific literature'' artifact class---not
    because its conclusions are ``true.''
    \item A government report is admissible because it has a document ID, is
    signed by an agency, and belongs to the ``official statistics'' artifact
    class---not because its numbers are ``correct.''
    \item Participants demonstrate engagement with admissible artifacts, not
    agreement with their conclusions.
\end{itemize}

\subsection{Test Grids as Admissibility Registries}

\begin{definition}[Token-Curated Test Grid]
A Token-Curated Test Grid (TCTG) is a governed registry that specifies which
classes of admissible artifacts may be referenced for a given proposal
domain.
Curation decisions are made by participants who stake tokens and are subject to
economic penalties if admitted artifacts are later shown to be malformed,
inauthentic, or procedurally invalid.

Test grids govern \emph{admissibility criteria} (format, provenance, relevance),
not semantic conclusions or interpretations.
\end{definition}

\textbf{Critical distinction}: Test grids do not define truth; they define the set
of artifacts that a decision process is permitted to reference.

Curators are slashed for admitting artifacts that:
\begin{itemize}
    \item Have invalid provenance (forged signatures, broken hash references)
    \item Violate format requirements (wrong artifact class for proposal type)
    \item Were retracted or invalidated by their issuing authority
\end{itemize}

Curators are \textit{not} slashed for admitting artifacts whose conclusions are
later contested, revised, or overturned through normal scientific or institutional
processes. The system does not adjudicate semantic disputes.

\subsection{Coherence as Process Quality}

\begin{definition}[Process Coherence]
The coherence score $\gamma$ does not measure correctness, factual truth, or
proposal merit. It measures statistical consistency and entropy quality of the
decision process given the declared admissible evidence and participation constraints.

Low coherence indicates process instability, coordinated behavior, or insufficient
entropy, independent of proposal content.
\end{definition}

A proposal can have high coherence and still be ``wrong'' by external standards.
A proposal can have low coherence despite being ``correct.'' The coherence score
measures whether the \textit{process} that produced the decision exhibited
properties consistent with legitimate deliberation.

\subsection{Scope of System Authority}

The governance system constrains \emph{how} decisions are made, not \emph{what}
decisions must conclude.

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{System Does} & \textbf{System Does Not} \\
\midrule
Verify artifact provenance & Evaluate artifact truth \\
Enforce participation requirements & Determine correct outcomes \\
Measure process consistency & Judge proposal merit \\
Bound individual influence & Override collective judgment \\
Detect coordinated manipulation & Censor unpopular positions \\
\bottomrule
\end{tabular}
\end{center}

This scope limitation is not a weakness but a design requirement. A system that
claimed semantic authority would be both philosophically indefensible and
practically capturable.

%------------------------------------------------------------------------------
\section{Augmented Democracy: Definition}
\label{sec:definition}
%------------------------------------------------------------------------------

\subsection{What Augmented Democracy Is Not}

\begin{itemize}
    \item \textbf{Not technocracy}: Experts do not override participants
    \item \textbf{Not algorithmic rule}: No AI makes final decisions
    \item \textbf{Not censorship}: All proposals enter the system
    \item \textbf{Not plutocracy}: Wealth does not determine influence
    \item \textbf{Not truth arbitration}: The system does not determine what is ``true''
\end{itemize}

\subsection{Definition}

\begin{definition}[Augmented Democracy]
A \textbf{constrained participation system} with admissibility gates, where:
\begin{enumerate}
    \item Participation requires registration (identity binding via dynamic NFTs)
    \item Voters must demonstrate engagement with proposal-relevant admissible artifacts
    \item Proposals traverse a filtering pipeline (review period with gatherers/curators)
    \item Votes are weighted by reputation and bounded by quadratic costs
    \item Acceptance requires coherence threshold satisfaction (process quality)
    \item All transitions produce cryptographic proofs (auditability)
    \item Credentials decay without ongoing participation (life-sustaining NFTs)
\end{enumerate}
\end{definition}

The key distinction from classical democracy: legitimacy derives from \textit{process invariants},
not outcome ratification. The ``augmented'' refers to procedural augmentation---ensuring voters
have verifiably engaged with relevant evidence before their input shapes collective decisions.

%------------------------------------------------------------------------------
% Section: Epistemic Infrastructure (imported)
%------------------------------------------------------------------------------
\input{section2-5-epistemic-infrastructure}

%------------------------------------------------------------------------------
% Section: Governance as a Control System (imported)
%------------------------------------------------------------------------------
\input{section3-governance-as-control-system}

%------------------------------------------------------------------------------
% Section: The Coherence Pipeline (bridge section)
%------------------------------------------------------------------------------
\input{section-bridge-coherence-pipeline}

%------------------------------------------------------------------------------
\section{Coherence Constraints in Democratic Systems}
\label{sec:coherence-constraints}
%------------------------------------------------------------------------------

\subsection{Coherence Functionals for Proposals}

Let $\mathcal{P}$ be the space of proposals and $\mathcal{C}: \mathcal{P} \rightarrow [0,1]$
a coherence functional. A proposal $p$ is \textit{on-manifold} if $\mathcal{C}(p) > \tau$
for threshold $\tau$.

In the implementation, $\mathcal{C}$ is realized through quantum confidence scoring:
\begin{equation}
    \mathcal{C}(p) = \frac{\gamma_p}{100}
\end{equation}
where $\gamma_p$ is computed from entropy variance across votes on $p$.

\textbf{Important}: $\gamma$ measures process quality, not outcome correctness.
High $\gamma$ indicates statistically independent participation with adequate
entropy. Low $\gamma$ indicates coordination, manipulation, or resource exhaustion.

\subsection{Bounded Influence}

No single participant can dominate outcomes. The weight function satisfies:
\begin{equation}
    w_i \in [w_{\min}, w_{\max}] \quad \forall i
\end{equation}
with $w_{\min} = 1$ (floor) and $w_{\max} = r_i \cdot 1.1$ (reputation cap with 10\% entropy bonus).

\subsection{Rollback and Retry Semantics}

Failed coherence checks do not corrupt state. The system remains at $s_t$ when:
\begin{itemize}
    \item $w_{\text{approve}} \leq w_{\text{reject}}$ (democratic failure)
    \item $\gamma \leq 50$ (coherence failure)
    \item Entropy pool exhausted (resource failure)
\end{itemize}

Submitters may revise and resubmit. The state machine supports retry without penalty.

\subsection{Limited Adversarial Feedback}

The system limits adversarial feedback by restricting rejection signals to typed
errors and coarse-grained status transitions.
While no distributed system can eliminate all side-channel information, this
design prevents gradient-style probing of coherence thresholds and minimizes
adaptive manipulation.

Malicious proposals trigger explicit rejection with typed errors. The error taxonomy
(Section~\ref{sec:governance-control}) ensures that:
\begin{enumerate}
    \item Attackers receive no fine-grained information about \textit{why} rejection occurred
    \item Legitimate users receive actionable feedback via different channels
    \item All rejections are logged for audit
\end{enumerate}

%------------------------------------------------------------------------------
\section{Quantum-Safe and Post-Quantum Alignment}
\label{sec:quantum}
%------------------------------------------------------------------------------

This is not a cryptography paper. However, the governance system inherits quantum resistance
from its substrate:

\subsection{Why Classical Assumptions Fail}

\begin{itemize}
    \item RSA/ECDSA signatures are broken by Shor's algorithm
    \item Hash-based commitments remain secure (Grover provides only quadratic speedup)
    \item Retroactive compromise: adversaries may record today's traffic for future decryption
\end{itemize}

\subsection{Post-Quantum Protections}

The Quantum Harmony implementation uses:
\begin{itemize}
    \item \textbf{SPHINCS+-256s}: Stateless hash-based signatures (NIST PQC standard)
    \item \textbf{Blake2-256}: Quantum-resistant hashing
    \item \textbf{QKD entropy}: True quantum randomness from KIRQ network
\end{itemize}

\subsection{Proof-of-Coherence vs.\ Proof-of-Work/Stake}

\begin{center}
\begin{tabular}{lccc}
\toprule
\textbf{Property} & \textbf{PoW} & \textbf{PoS} & \textbf{PoC} \\
\midrule
Energy cost & High & Low & Low \\
Plutocracy risk & Medium & High & Low \\
Quantum resistance & None & None & Full \\
Sybil resistance & Hash rate & Stake & Coherence \\
Manipulation detection & None & None & Built-in \\
\bottomrule
\end{tabular}
\end{center}

Proof-of-Coherence detects manipulation \textit{before} state transition, whereas PoW/PoS
detect only after finalization (if at all).

%------------------------------------------------------------------------------
\section{Historical Implementation: From Concept to Quantum Infrastructure}
\label{sec:history}
%------------------------------------------------------------------------------

The augmented democracy framework has evolved through eight years of development,
from theoretical conception to production deployment.

\subsection{Conceptual Foundation (2017)}

The original framework was published in August 2017 as ``A Machine-Based Societal
Model for Curbing Citizen Cynicism''~\cite{cormier2017augmented}. Key concepts
established:

\begin{itemize}
    \item \textbf{Test grids}: Voters must demonstrate engagement with relevant evidence
    \item \textbf{Mechanical humans}: Low-barrier contribution tasks for universal participation
    \item \textbf{Operating system metaphor}: Governance as a self-regulating system
    \item \textbf{Blockchain validation}: Immutable record of all decisions
    \item \textbf{Official as safeguard}: Human oversight of machine recommendations
\end{itemize}

The 2017 paper explicitly framed democracy as ``critical infrastructure'' requiring
engineering discipline---a perspective that remains central to the current implementation.

\subsection{EOS Prototype and Oracle Integration (2020--2021)}

The first production implementation deployed as an EOS smart contract:

\begin{itemize}
    \item \textbf{augdemocracy.cpp}: Core smart contract with registration and voting
    \item \textbf{Token Curated Test Grids}: KILT-inspired gatherer/curator structure~\cite{kilt2020}
    \item \textbf{Oracle integration}: Decentralized artifact sourcing via oracle networks
    \item \textbf{Dynamic NFTs}: Early credential management prototypes
    \item \textbf{Quadratic voting}: Whale resistance mechanisms
\end{itemize}

The EOS implementation validated the admissibility gate concept in production,
demonstrating that artifact-engagement verification was technically feasible and user-acceptable.
Concurrent research into Polkadot ecosystem oracle solutions (including Kylin Network,
a Polkadot parachain for cross-chain data feeds) informed the design of the
decentralized artifact-sourcing layer.

\subsection{Substrate Migration (2022--2023)}

Migration to the Substrate framework enabled:

\begin{itemize}
    \item \textbf{Pallet architecture}: Modular, upgradeable governance components
    \item \textbf{Cross-chain compatibility}: Polkadot ecosystem integration
    \item \textbf{Runtime upgrades}: Governance system self-modification
    \item \textbf{Improved NFT standards}: FRAME-native credential tokens
\end{itemize}

The Substrate pallet (\texttt{pallet-quantum-democracy}) preserved all EOS-era
features while adding formal verification capabilities.

\subsection{Quantum Harmony Integration (2024--2025)}

Current production deployment on Quantum Harmony blockchain:

\begin{itemize}
    \item \textbf{Quantum entropy pool}: True randomness from KIRQ network
    \item \textbf{Coherence-based consensus}: Replaces stake-based finality
    \item \textbf{Post-quantum signatures}: SPHINCS+-256s for credential integrity
    \item \textbf{QKD-protected channels}: Quantum key distribution for artifact delivery
    \item \textbf{Toshiba/Crypto4A integration}: Hardware security module support
\end{itemize}

\subsection{Continuity of Core Principles}

Across all implementations, core principles remain constant:

\begin{center}
\begin{tabular}{lcccc}
\toprule
\textbf{Principle} & \textbf{2017} & \textbf{EOS} & \textbf{Substrate} & \textbf{QH} \\
\midrule
Artifact-gated voting & Concept & Implemented & Enhanced & Production \\
Dynamic credentials & Concept & Prototype & NFT-based & Life-sustaining \\
Quadratic bounds & Concept & Implemented & Integrated & + Entropy \\
Coherence threshold & Implicit & Partial & Formal & Quantum \\
Official safeguard & Central & Preserved & Root-only & Emergency \\
\bottomrule
\end{tabular}
\end{center}

This evolution demonstrates that augmented democracy is not speculative---it is
iteratively refined infrastructure with continuous production deployment since 2020.

%------------------------------------------------------------------------------
\section{Failure Modes and Emergency Governance}
\label{sec:failure}
%------------------------------------------------------------------------------

\subsection{When Coherence Fails}

Coherence failure ($\gamma \leq 50$) indicates:
\begin{enumerate}
    \item \textbf{Coordinated attack}: Sybil voters with correlated entropy
    \item \textbf{Entropy exhaustion}: Insufficient quantum randomness
    \item \textbf{System compromise}: Entropy source manipulation
\end{enumerate}

Coherence failure does \textit{not} indicate that the proposal is wrong, harmful,
or should be rejected on substantive grounds. It indicates only that the
\textit{process} exhibited statistical anomalies.

\subsection{Emergency Committee Override}

For critical failures, the system supports:
\begin{lstlisting}[language=Rust]
ensure_root(origin)?;  // Root-only operations
\end{lstlisting}

This is the ``break glass'' mechanism. Root authority can:
\begin{itemize}
    \item Replenish entropy pool
    \item Pause voting
    \item Trigger manual review
\end{itemize}

Root cannot:
\begin{itemize}
    \item Directly approve/reject proposals
    \item Modify vote records
    \item Alter coherence thresholds retroactively
\end{itemize}

\subsection{Human-in-the-Loop Escalation}

When automated coherence checks fail repeatedly, the system escalates to human review:
\begin{enumerate}
    \item Proposal flagged for manual assessment
    \item Validator committee convenes (off-chain)
    \item Committee issues signed recommendation
    \item Recommendation enters normal voting pipeline
\end{enumerate}

This preserves the coherence constraint while acknowledging that some edge cases
require human judgment.

\subsection{Response Windows}

\begin{center}
\begin{tabular}{lcc}
\toprule
\textbf{Event} & \textbf{Detection} & \textbf{Response} \\
\midrule
Low entropy & Immediate & Auto-pause voting \\
Coherence failure & At finalization & Proposal held \\
Repeated failures & 3 consecutive & Escalate to committee \\
System compromise & Manual detection & Emergency halt \\
\bottomrule
\end{tabular}
\end{center}

%------------------------------------------------------------------------------
% User Experience and Agent Delegation
%------------------------------------------------------------------------------
\input{section-ux-friction}

%------------------------------------------------------------------------------
\section{Conclusion: Democracy as Infrastructure}
\label{sec:conclusion}
%------------------------------------------------------------------------------

Democracy is no longer a philosophical abstraction. It is \textbf{critical infrastructure}.

The systems we use to make collective decisions are under adversarial load from state actors,
AI-generated influence, and the fundamental speed/quality tradeoff of digital communication.
Traditional democratic theory offers no defense against these threats because it treats
legitimacy as a property of outcomes rather than processes.

This paper has presented an alternative: \textit{coherence-constrained democratic systems}
with \textit{procedural infrastructure}, where:
\begin{enumerate}
    \item Proposals are state transitions in a formal control system
    \item Participants hold dynamic credentials that evolve with contribution
    \item Voters must demonstrate engagement with admissible artifacts (procedural gate)
    \item Quadratic voting costs bound plutocratic influence
    \item Deliberation is a filtering operation with minimum dwell time
    \item Approval requires both majority support \textit{and} coherence threshold
    \item All transitions produce cryptographic proofs
    \item Credentials decay without ongoing participation (life-sustaining NFTs)
\end{enumerate}

The central thesis is that \textbf{democratic legitimacy is a measurable property of
process quality, independent of specific outcomes}.

This is not ideology. It is engineering.

\textbf{The governance system constrains how decisions are made, not what decisions
must conclude.}

The framework has evolved through eight years of development---from the 2017 conceptual
paper through EOS smart contract prototypes to the current Quantum Harmony implementation.
Each iteration validated core principles while adding cryptographic hardening. Combined
with prior work on ERLHS (coherence in AI), Karmonic Mesh (geometric substrate), and
Proof of Coherence (distributed validation), this framework provides a complete architecture
for augmented democracy as 21st-century infrastructure.

The procedural stack---token-curated test grids, dynamic credential NFTs, quadratic voting,
coherence thresholds, and accountability mechanisms---transforms voting from opinion
aggregation into \textit{structured preference revelation}. This is the augmentation that
gives augmented democracy its name: not technological enhancement of voting mechanics,
but procedural elevation of participation quality.

The friction inherent in this architecture is addressed through agent-mediated
participation: AI agents that navigate the coherence pipeline on behalf of human
principals. Humans set values and priorities; agents handle the mechanics. This
creates a new division of labor---humans as value-setters, agents as executors---
with coherence constraints applying at both levels. The ERLHS framework ensures
agent coherence; the democratic framework ensures process coherence. Together,
they enable participation at scale without sacrificing procedural quality.

The ultimate vision: a system where legitimate collective decisions emerge from
coherence-preserving processes, mediated by trustworthy agents, grounded in
verifiable artifacts, and accountable to human values. This is democracy as infrastructure---
engineered, deployable, and resistant to adversarial conditions.

%------------------------------------------------------------------------------
% References
%------------------------------------------------------------------------------
\bibliographystyle{plain}
\begin{thebibliography}{99}

\bibitem{cormier2017augmented}
Cormier, S. (2017).
\textit{A Machine-Based Societal Model for Curbing Citizen Cynicism}.
Unpublished manuscript, August 2017.

\bibitem{cormier2025erlhs}
Cormier, S. (2025).
\textit{ERLHS: A Hamiltonian Framework for Coherence-Preserving Machine Intelligence}.
Zenodo. \url{https://doi.org/10.5281/zenodo.17928909}

\bibitem{cormier2025karmonic}
Cormier, S. (2025).
\textit{Karmonic Mesh: Spectral Consensus on Toroidal Manifolds}.
Zenodo. \url{https://doi.org/10.5281/zenodo.17928991}

\bibitem{cormier2025poc}
Cormier, S. (2025).
\textit{Proof of Coherence: QKD-Based Distributed Consensus}.
Zenodo. \url{https://doi.org/10.5281/zenodo.17929054}

\bibitem{cormier2025toroidal}
Cormier, S. (2025).
\textit{Toroidal Mesh: 10K TPS with SPHINCS+ via Parallel Verification}.
Zenodo. \url{https://doi.org/10.5281/zenodo.17931222}

\bibitem{cormier2025governance}
Cormier, S. (2025).
\textit{Toroidal Governance: Tonnetz Manifold Democratic Infrastructure}.
Zenodo. \url{https://doi.org/10.5281/zenodo.17929091}

\bibitem{buterin2019quadratic}
Buterin, V., Hitzig, Z., \& Weyl, E. G. (2019).
\textit{A Flexible Design for Funding Public Goods}.
Management Science, 65(11), 5171--5187.

\bibitem{kilt2020}
BOTLabs GmbH. (2020).
\textit{KILT Protocol White Paper: Credentials for Web 3.0}.
Berlin, Germany.
\url{https://kilt-protocol.org/files/KILT-White-Paper.pdf}

\end{thebibliography}

\end{document}
